---
title: "Chapter 3 Exercises"
author: "Derek Chiu"
date: "July 20, 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 3.1.7 Exercises

1. Fix each of the following common data frame subsetting errors:

    `mtcars[mtcars$cyl = 4, ]`  
    `mtcars[-1:4, ]`  
    `mtcars[mtcars$cyl <= 5]`  
    `mtcars[mtcars$cyl == 4 | 6, ]`  
  
    > `mtcars[mtcars$cyl == 4, ]`  
      `mtcars[1:4, ]`  
      `mtcars[mtcars$cyl <= 5, ]`  
    `mtcars[mtcars$cyl == 4 | mtcars$cyl == 6, ]`
        
2. Why does `x <- 1:5`; `x[NA]` yield five missing values? (Hint: why is it different from `x[NA_real_]`?)

    >  `NA` is a logical that always replaces a vector with `NA`. Coercion doesn't occur with `NA_real_`.

3. What does `upper.tri()` return? How does subsetting a matrix with it work? Do we need any additional subsetting rules to describe its behaviour?

    `x <- outer(1:5, 1:5, FUN = "*")`  
    `x[upper.tri(x)]`
    
    > A matrix of logicals where the upper triangular is `TRUE`. It returns elements that belong to the upper triangular. The elements are returned as a vector in column order.
    
4. Why does `mtcars[1:20]` return a error? How does it differ from the similar `mtcars[1:20, ]`?

    > There aren't 20 columns in `mtcars`. `mtcars[1:20, ]` subsets the first 20 rows and all columns.

5. Implement your own function that extracts the diagonal entries from a matrix (it should behave like `diag(x)` where `x` is a matrix).

```{r}
diagonal <- function(x) {
  return(x[row(x) == col(x)])
}
x <- matrix(1:25, nrow = 5)
diagonal(x)
diagonal(mtcars)
```

6. What does `df[is.na(df)] <- 0` do? How does it work?

    > Replaces all entries of `df` which are `NA` with 0. Matrix subsetting is used since `is.na(df)` is a matrix of logicals.

# 3.2.4 Exercises 

1. Given a linear model, e.g., `mod <- lm(mpg ~ wt, data = mtcars)`, extract the residual degrees of freedom. Extract the R squared from the model summary (`summary(mod)`)

```{r}
mod <- lm(mpg ~ wt, data = mtcars)
mod$resid
summary(mod)$r.squared
```

# 3.4.9 Exercises

1. How would you randomly permute the columns of a data frame? (This is an important technique in random forests.) Can you simultaneously permute the rows and columns in one step?

```{r}
set.seed(1)
x <- matrix(1:25, nrow = 5)
x[, sample(ncol(x))]
x[sample(nrow(x)), sample(ncol(x))]
```

2. How would you select a random sample of m rows from a data frame? What if the sample had to be contiguous (i.e., with an initial row, a final row, and every row in between)?

```{r}
x <- mtcars
m <- 5
x[sample(nrow(x), m), ]
x[do.call(seq, as.list(sort(sample(nrow(x), 2, replace = TRUE)))), ]
```

3. How could you put the columns in a data frame in alphabetical order?

```{r}
x <- data.frame(b = 1:5, c = 6:10, a = 11:15)
x[, sort(names(x))]
```
